%
\pagebreak
\section{Publications}
\label{sec:publications}
%
\small
\newcommand{\myitemsep}{0mm}
%
\renewcommand{\refname}{\normalsize{Journaux internationaux}}
\begin{thebibliography}{1}
\setlength{\itemsep}{\myitemsep}
%
\bibitem[Velut et al., 2007]{VEL07}
\textbf{J.~Velut}, H.~Benoit-Cattin, and C.~Odet.
\newblock Locally regularized smoothing B-snake.
\newblock {\em EURASIP Journal on Advances in Signal Processing},
2007:Article ID 76241, 12 pages, 2007.
%
\end{thebibliography}
%
\renewcommand{\refname}{\normalsize{Journaux nationaux}}
\vspace{-10pt}
\begin{thebibliography}{1}
\setlength{\itemsep}{\myitemsep}
%
\bibitem[Coatrieux et al., 2010]{COA10}
J.-L. Coatrieux, \textbf{J.~Velut}, J.-L. Dillenseger, and C.~Toumoulin.
\newblock [From medical
  imaging to image-guided therapy],
\newblock \emph{Med Sci} (Paris) 26~(12) (2010) 1103--1109.
%
\bibitem[Velut et al., 2011]{VEL11}
\textbf{J.~Velut}, P.-A.~Lentz, D.~Boulmier, J.-L.~Coatrieux, and C.~Toumoulin.
\newblock Assessment of qualitative and quantitative features in coronary artery
MRA,
\newblock \emph{IRBM}, soumis. 
\end{thebibliography}
%
\renewcommand{\refname}{\normalsize{Conf\'erences internationales avec
		    comit\'e de lecture }}
\vspace{-10pt}
\begin{thebibliography}{6}
\setlength{\itemsep}{\myitemsep}
%
\bibitem[Velut et al., 2006a]{VEL06.1}
\textbf{J.~Velut}, H.~Benoit-Cattin, and C.~Odet.
\newblock Locally regularized snakes through smoothing B-spline 
filtering.
\newblock In {\em EUSIPCO}, Sept. 2006.
%
\bibitem[Velut et al., 2006b]{VEL06.2}
\textbf{J.~Velut}, H.~Benoit-Cattin, and C.~Odet.
\newblock Segmentation by smoothing B-spline active surface.
\newblock In {\em ICIP},
pages 209--212, Oct. 2006.
%
\bibitem[Velut et al., 2008]{VEL08}
\textbf{J.~Velut}, H.~Benoit-Cattin, and C.~Odet.
\newblock IIR filtering of surface meshes for the regularization of 
deformable models.
\newblock In {\em ICIP}, 2008.
%
\bibitem[Du et al., 2008]{DU08}
X.~Du, \textbf{J.~Velut}, R.~Bolbos, O.~Boeuf, H.~Benoit-Cattin, and C.~Odet.
\newblock 3-D knee cartilage segmentation using a smoothing B-spline
active surface.
\newblock In {\em ICIP}, 2008.
%
\bibitem[Garcia et al., 2010]{GAR10.1}
M.-P.~Garcia, C.~Toumoulin, P.~Haigron, \textbf{J.~Velut}, M.~Garreau,
D.~Boulmier,
Coronary veins tracking from MSCT using a minimum cost approach.
\newblock In {\em ISBI}, 2010, pp. 17--20.
%
\bibitem[Garreau et al., 2010]{GAR10.2}
M.~Garreau, M.-P. Garcia, F.~Tavard, A.~Simon, J.~Fleureau, \textbf{J.~Velut},
D.~Boulmier, P.~Haigron, C.~Toumoulin, and C.~Leclercq. 
\newblock Abilities of cardiac msct imaging to provide useful anatomical and
functional information for cardiac resynchronization therapy optimization.
\newblock In {\em Computing in Cardiology}, 2010, pp. 237--240.
%
\bibitem[Velut et al., 2010a]{VEL10.1}
\textbf{J.~Velut}, C.~Toumoulin, J.-L. Coatrieux.
\newblock 3D coronary structure tracking algorithm with regularization and
multiple hypotheses in MRI.
\newblock In {\em ISBI}, 2010, pp. 37--40.
%
\bibitem[Velut et al., 2010b]{VEL10.2}
\textbf{J.~Velut}, P.~Lentz, C.~Philipot, M.~Garcia, and C.~Toumoulin.
\newblock A qualitative and quantitative study of coronary artery MRA, 
\newblock in: \emph{EMBC}, 2010, pp. 5724--5727.
\end{thebibliography}
%
\renewcommand{\refname}{\normalsize{Conf\'erences internationales}}
\vspace{-10pt}
\begin{thebibliography}{2}
\setlength{\itemsep}{\myitemsep}
%
\bibitem[Camara et al., 2010]{CAM10}
O.~Camara, C.~Riccobene, D.~Romero, R.~Sebasti\~an, F.~Sukno, C.~Butakoff,
  M.~de~Craene, P.~Omedas, A.~F. Frangi, \textbf{J.~Velut}, C.~Philipot,
C.~Toumoulin,
  B.~Rodriguez, P.~Lamata, S.~Duckett, R.~Razavi, A.~Groth, J.~Weese, and
  O.~Ecabert.
\newblock Integrative software framework for a better understanding,
  patient selection and planning of Cardiac Resynchronization Therapy patients,
\newblock in: \emph{VPH Conference}, 2010.
\bibitem[Velut et al., 2010c]{VEL10.3}
\textbf{J.~Velut}, C.~Philipot, C.~Riccobene, P.~Omedas, A.~F. Frangi, and
C.~Toumoulin.
\newblock  Prototype tool for the extraction of the coronary vessels centreline,
\newblock in: \emph{VPH Conference}, 2010.
\end{thebibliography}
%
\renewcommand{\refname}{\normalsize{Conf\'erences nationales avec
		    comit\'e de lecture }}
\vspace{-10pt}
\begin{thebibliography}{1}
\setlength{\itemsep}{\myitemsep}
%
\bibitem[Kpozehoue et al., 2011]{KPO11}
A.~Kpozehoue, \textbf{J.~Velut}, P.-A. Lentz, and C.~Toumoulin.
\newblock Calcul de cylindricit\'e
  bas\'e sur les moments g\'eom\'etriques, 
\newblock in: \emph{RITS}, 2011.
\end{thebibliography}
%
\renewcommand{\refname}{\normalsize{Publications en ligne }}
\begin{thebibliography}{1}
\vspace{-10pt}
\setlength{\itemsep}{\myitemsep}
%
\bibitem[Velut, 2011]{VEL11.1}
\textbf{J.~Velut}.
\newblock Explicit deformable model in VTK,
\newblock \emph{The VTK Journal}, 2011, \url{http://hdl.handle.net/10380/3251}
\end{thebibliography}
%